\bibliographystyle{plain}
\bibliography{references}

\begin{thebibliography}{9}

\bibitem{Richard}
R. Schreier and G. C. Temes,
\textit{"Understanding Delta-Sigma Data Converters"},
New York,
IEEE press,
Wiley-Interscience,
ISBN:0-471-46585-2,
2005,

\bibitem{for_pro}
Duvarahan K. \textit{Design and Behavioral Modeling of a High Resolution, Discrete-Time Delta-Sigma ADC }, NTNU, 2017

\bibitem{Ovi}
Ovidiu B, Johan H.h, 
\textit{"Systematic Design of Sigma-Delta A/D Converters"},
Kluwer Academic Publishers,
ISBN: 1-4020-7945-1

\bibitem{Allen}
Allen P.E,  Holberg D.R, 
\textit{"CMOS Analog Circuit Design"},
Oxford University press,
ISBN: 0-19-51 1644-5

\bibitem{Johns}
Johns D.A, Martin K, 
\textit{"Analog Integrated Circuit Design"},
John Wiley and Sons inc. ,
ISBN: 984-12-647-0

\bibitem{Razavi}
Razavi B, 
\textit{"Principles of Data Conversion System Design"}, 
IEEE press,
ISBN : 0-7803-1093-4

\bibitem{Barker}
Barker J.R,
\textit{"CMOS Mixed-Signal Circuit Design" },
IEEE press
ISBN: 0-471-22754-4

\bibitem{deltapic}
M.Ortmanns and F.Gerfers,
\textit{"Continuous-Time Sigma-Delta A/D Conversion
Fundamentals,PerformanceLimits and Robust Implementations"},
Secaucus,
NJ,USA:
Springer-Verlag
NewYork,
Inc.,
ISBN:978-3-540-28406-2.
Springer Series in Advanced Micro electronics
Volume21,
2006.

\bibitem{charge_pump}
B.R. Gregoire,
\textit{A switched capacitor regulated charge pump power supply},
Custom Integrated Circuits Conference, 2005, Proceedings of the IEEE 2005,
ISBN: 0-7803-9 023-7

\bibitem{SQNR}
J. V. De la C. Marin,
\textit{INTEGRATED CIRCUIT DESIGN OF SIGMA-DELTA MODULATOR FOR
ELECTRIC ENERGY MEASUREMENT APPLICATIONS},
instituto alberto luiz coimbra de pós-graduação e pesquisa de engenharia,
RIO DE JANEIRO, RJ – BRASIL,
2013

\bibitem{William}
Schweber, William L.,
\textit{Integrated Circuits for Computers: Principles and Applications},
McGraw-Hill, pp. 157-158,
ISBN: 978-0-070-53624-1

\bibitem{Malo}
Maloberti F, 
\textit{"Data Converters"}
Dordrecht, Netherlands,
Springer 2007,
ISBN: 978-0387324852.

\bibitem{load}
Jian X, Hanqing W, Xiaobo W,
\textit{A 20 micro 95dB DR Single-Bit Delta-Sigma Modulator for Portable Measurement Applications},
Proceedings of the international MultiConference of Engineers and Computer Scientists 2010 Vol 2,
IMECS 2010, March 17-19, 2010, Hong Kong

\bibitem{gm_id_1}
F.Silveira, D.Flandre and P.G.A Jespers
\textit{A $g_m/I_D$ Based Methodology for the Design of CMOS Analog Circuits and Its application to the Synthesis of a Silicon-on-Insulator Micropower OTA},
IEEE journal of solid-state circuits, VOL. 31 NO. 9 September 1996.


\bibitem{first_delta}
H.Inose, Y.Yasuda and J.Murakami,
\textit{"A Telemetry System by Code Modulation - Delta-Sigma Modulation"},
Space Electronics and Telemetry,
IRE Transactions on vol.
SET-8, pp. 204-209,
1962

\bibitem{two_stage_1}
Rio.F, R.Mederio Hidalgo, F. Perez-Verdu, B. Rosa Ultrera, J.M. Rodriquez-Vazquez,
\textit{CMOS Cascade Sigma-Delta Modulators for Sensors and Telecom Error Analysis and Practical Design },
Springer Netherlands, 2006,
ISBN: 978-1-4020-4776-3

\bibitem{Plass}
Plassche R., 
\textit{"CMOS Integrated Analog-to-Digital and Digital-to-Analaog converters"},
Boston, Kluwer Academic Publisers, 2003,
ISBN: 978-3-540-28473-4

\bibitem{corr}
 C.C. Enz ; G.C. Temes,
 \textit{"Circuit techniques for reducing the effects of op-amp imperfections: autozeroing, correlated double sampling, and chopper stabilization"},
 Proceedings of the IEEE,
 vol 84, issue 11,
 pp. 1584-1614,
 1996

\bibitem{phase}
David F.S and Kaufman M, 
\textit{Handbook of operational amplifier circuit design},
NY: Mc-Graw-Hill,
Sec. 3-4, 
ISBN 0-07-061797-X

\bibitem{Lee}
K.-H. Chao, S.Nadeem, W.Lee and C.Sodini, 
\textit{"A higher order topology for interpolative modulators for oversampling A/D converters"},
Circuits and Systems, IEEE Transactions on, vol. 37, pp. 309-318 mar 1990.

\bibitem{cds}
W. H. White, D. R. Lampe, F. C. Blaha, and 1. A. Mack, \textit{“Characterization
of surface channel CCDimage arrays at low light levels"}
IEEE J. Solid-State Circuits, vol. SC-9, pp. 1-14, Feb. 1974.

\bibitem{private}
Private communication with \textit{Microchip}.

\bibitem{Grey}
P. R. Grey, P. J. Hurst, S. H. Lewis, R. Meyer,
\textit{Analysis and Design of Analog Integrated Circuits},
John Wiley Sons, 5th edition 2009,
ISBN: 978-0470245996


\bibitem{two_stage_2}
Yao I., Steyaert M., Sansen W., 
\textit{Low-power low-voltage sigma-delta modulators in nanometer CMOS},
Springer Netherlands, 2006,
ISBN: 978-1-4020-4140-2

\bibitem{gm_id_2}
H.D. Danmark, S.Bensalem, S.Zouari and M.Loulou
\textit{Design of Folded Cascode OTA in Different Regions of Operation though $g_m/I_D$ Methodology},
World Academy of Science, Engineering and Technology International Journal of Electrical and Computer Engineering, Vol. 2, No. 9, 2008

\bibitem{ref_1}
Mike.R, Nicholas R.V.B, Patrick R, Robert G, James C, John R.H,
\textit{A 16-b 160-kHz CMOS A/D Converter Using Sigma-Delta Modulation},
IEEE Journal of Solid-State Circuits, VOL 25, Issue 2, April 1990, pp. 431-440.

\bibitem{tool}
R.Schreier,
\textit{Delta-Sigma Toolbox},
2010
[Online]
Avaliable:
\url{http:www.mathworks.com/matlabcentral/fileexchange/19}.

\bibitem{comparator}
Ho J, Luong H,
\textit{A 3-V 1.47mW 120MHz Comparator for Use in Pipline ADC},
Proceedings of IEEE Asia-Pacific Conference on Circuits and System 96, p. 413-416, November 1996

\bibitem{adaptive}
Antonio J.L.M, Sushmita B, Jaime R.A, Ramon G.C,
\textit{Low-Voltage Super CLass AB CMOS OTA Cells With Very High Slew Rate and Power Efficiency},
IEEE J. Solid-State Circuits, vol 40 no 5, pp. 1068-1077, October 2005.

\bibitem{ref_2}
Bernhard E.B, Bruce A.W,
\textit{The Design of Sigma-Delta Modulation Analog-to-Digital Converters},
IEEE, Journal of Solid-State Circuits, VOL 23, NO 6, December 1998, pp. 1298-1308.

\bibitem{ref_3}
Sumit K.N, 
\textit{Design of a 14-bit fully differential discrete time delta-sigma modulator},
Rochester Institute of Technology, RIT Scholar works, 11.15.2006.
\bibitem{ref_4}
Yongsheng W, Yuanhong L, Mingyan Y.,
\textit{A 16 bit low voltage low power Delta Sigma modulator}.
Proceedings of 2011 International Conference on Electronics and Mechanical Engineering and Information Technology, VOL 6, pp. 3178-3181, 2011.

\bibitem{ref_5}
Da Q., Yuan-wen L., Long C., Jun X., Fan Y., Jun-yan R.,
\textit{An ultra low power sigma-delta modulator for hearing aid double-sampling},
IEEE, 8th International Conference on ASIC, pp. 1141-1144, 2009.

\bibitem{ref_6}
Zhijun L., Benoit G., Mohamad S., 
\textit{A 16-bit sigma-delta modulator for low power medical implantable sensors}
IEEE, International Conference on Electronics, Circuits and System, pp. 1-4, 2005

\bibitem{ref_7}
Joshua L., DAvid A. J., 
\textit{A frequency-scalable 15-bit incremental ADC for low power sensor applications},
IEEE, International Symposium on Circuits and System, pp. 2418-2421, 2010.

\bibitem{ref_8}
Serena P., Francesco C. Chris V. H., Eugenio C., Arthur H. M. van R., 
\textit{A Power-Optimal Design Methodology for High-Resolution Low-Bandwidth SC Delta-sigma Modulators},
IEEE Transactions on Instrumentation and Measurement, VOL. 61, Issue. 11, pp. 2896-2904, 2012

\bibitem{ref_9}
Wei L., Peiyuan W., Pingfen L.,
\textit{A 0.8-V 48uW 82dB SNDR 10-kHz bandwidth delta-sigma modulator},
IEEE, international Symposium, pp. 89-91, 2012
\end{thebibliography}

